Using temperature distributions of active regions to investigate flare activity

### 2015-03-12 paper.tex
More minor intro edits
References to paper I redone

Studies of coronal temperatures date back several decades. % Stick some references here to early DEM studies
However, the Atmospheric Imaging Assembly (AIA) \citep{Lemen2011} which began observing the Sun in 2010 allows unprecedented access to observations with very high spatial and temporal resolution.
This allos us to investigate temperature distributions on small spatial scales with high cadence. % Don't much like this sentence, but oh well
The six Fe-based EUV channels of AIA also provide greater constraints on temperature solutions than previous coronal imagers \citep{Guennou2012, Guennou2012a}.

@@

Although it is faster than others of its kind, the temperature-calculating method used here requires a very large amount of AIA data, which can take a long time to download and process.
As such this is work investigates only a relatively small number of flares and the results should not be considered definitive.
Rather they are a proof of concept; they demonstrate the type of study made available by fast temperature analysis of the corona, which has only been made possible by the high-quality data provided by AIA.

%===========================================================================
\section{Method}
\subsection{Temperature analysis}
The core of this analysis is the temperature map method described by \cite{Leonard} (henceforth Paper I).
Briefly, this method compares the relative brightnesses in each AIA wavelength channel at a given time and infers the best-fitting temperature from that comparison. % This can be phrased more descriptively
This allows the temperature of the corona to be estimated for every pixel of an AIA image, resulting in very high resolution temperature maps.
Crucially, this method produces temperature maps extremely quickly, which allows us to investigate coronal temperatures during localised dynamic events such as flares.
With other, slower methods, such studies are infeasible due to the computation time required.
An example temperature map is shown in Figure \ref{fig:example_tmap}.

The Paper I method also allows easy `tracking' of solar regions by cropping the temperature map around a given pair of Carrington heliographic coordinates, which rotate at approximately the rate of solar rotation.
This tracking is demonstrated in Figures \ref{fig:trackdemo1} and \ref{fig:trackdemo2}, each of which shows a cropped region of an AIA 17.1nm image containing active region AR11158, the corresponding temperature map and a larger 17.1nm image showing the location of the region in the corona.

@@

\subsection{Active region analysis}
The temperature map method described in Paper I was used to investigate the temperatures of the active regions associated with flares which occured during February 2011. % And March, hopefully
This month was chosen because several flares occured during this time with a wide range of peak fluxes. % These months
The flares detected included many small flares (B and C class) as well as several larger M class flares and a single X class flare. % Double check these numbers to include March

@@

%===========================================================================
\section{Discussion and conclusions}
From this study, it appears that there is no clear link between solar flares and coronal temperatures.
This is probably mostly due to the relatively small number of flares studied - a much larger sample size would have to be used to properly determine any link or lack thereof.
In particular, this study only included a single X class flare, which as the most energetic are the kind we would most wish to predict.
Future works should therefore aim to consider more large flares.
Non-flaring active regions should also be taken into account and compared against the results presented here.
However, this work does demonstrate that it is now possible to study temperature distributions of the corona in high resolution and on short timescales using fast temperature analysis tools such as the one described in Paper 1.

>>>>

Studies of coronal temperatures date back several decades. % Stick some references here to early DEM studies
However, the Atmospheric Imaging Assembly (AIA; \cite{Lemen2011}) which began observing the Sun in 2010 allows unprecedented access to observations with very high spatial and temporal resolution.
This allos us to investigate temperature distributions on small spatial scales with high cadence. % Don't much like this sentence, but oh well
The six Fe-based EUV channels of AIA also provide greater constraints on temperature solutions than previous coronal imagers \citep{Guennou2012, Guennou2012a}.

@@

Although it is faster than others of its kind, the temperature-calculating method used here requires a very large amount of AIA data, which can take a long time to download and process.
As such this work investigates only a relatively small number of flares and the results should not be considered definitive.
Rather they are a proof of concept; they demonstrate the type of study made available by fast temperature analysis of the corona, which has only been made possible by the high-quality data provided by AIA.

%===========================================================================
\section{Method}
\subsection{Temperature analysis}
The core of this analysis is the temperature map method described by \cite{Leonard} (henceforth Paper I). \defcitealias{Leonard}{Paper I}
Briefly, this method compares the relative brightnesses in each AIA wavelength channel at a given time and infers the best-fitting temperature from that comparison. % This can be phrased more descriptively
This allows the temperature of the corona to be estimated for every pixel of an AIA image, resulting in very high resolution temperature maps.
Crucially, this method produces temperature maps extremely quickly, which allows us to investigate coronal temperatures during localised dynamic events such as flares.
With other, slower methods, such studies are infeasible due to the computation time required.
An example temperature map is shown in Figure \ref{fig:example_tmap}.

The \citetalias{Leonard} method also allows easy `tracking' of solar regions by cropping the temperature map around a given pair of Carrington heliographic coordinates, which rotate at approximately the rate of solar rotation.
This tracking is demonstrated in Figures \ref{fig:trackdemo1} and \ref{fig:trackdemo2}, each of which shows a cropped region of an AIA 17.1nm image containing active region AR11158, the corresponding temperature map and a larger 17.1nm image showing the location of the region in the corona.

@@

\subsection{Active region analysis}
The temperature map method described in citetalias{Leonard} was used to investigate the temperatures of the active regions associated with flares which occured during February 2011. % And March, hopefully
This month was chosen because several flares occured during this time with a wide range of peak fluxes. % These months
The flares detected included many small flares (B and C class) as well as several larger M class flares and a single X class flare. % Double check these numbers to include March

@@

%===========================================================================
\section{Discussion and conclusions}
From this study, it appears that there is no clear link between solar flares and coronal temperatures.
This is probably mostly due to the relatively small number of flares studied - a much larger sample size would have to be used to properly determine any link or lack thereof.
In particular, this study only included a single X class flare, which as the most energetic are the kind we would most wish to predict.
Future works should therefore aim to consider more large flares.
Non-flaring active regions should also be taken into account and compared against the results presented here.
However, this work does demonstrate that it is now possible to study temperature distributions of the corona in high resolution and on short timescales using fast temperature analysis tools such as the one described in \citetalias{Leonard}.
